\begin{abstract}
The online electronic sports (eSports) community has grown significantly 
over the past decade, with over 2 billion video game players as of 2015. 
Currently, these players spend more than 3 billion hours per week spread 
among playing computer and console games. Recent estimates show that 
this time in-game generates over 400 Terabytes of data per week.  
These numbers are expected to increase dramatically as the growth 
rate of the eSports community continues to rise.  The potential applications 
for this deluge of data are vast, with including translating many of the data 
analysis applications from traditional sports.

Data analysis has been used in the traditional sports settings to predict 
useful statistics about sports games even before the games occur.  
Machine learning models benefit from the large amounts of data available 
in sports game histories, enabling data scientists to employ a variety of tools 
to 
predict the winning team, the end-game score, and even 
individual player performances of future games.  As in most applications, 
the predictions are not 100\% accurate but still give meaningful statistics.

Machine learning is a natural application for the emerging eSports field 
given the large amounts of data available.  Our work applies some 
machine learning techniques to draw a parallel between eSports and 
traditional sports.  We show that by using the data available for League of Legends, 
we can extract useful insights to predict win-rates before the games occur.
\end{abstract}

